### 2015-12-20 outline.tex
add motivation to outline

>>>>

\vskip.3in
Need to motivate question
\begin{itemize}
	\item How long do deviations from trade agreement tariffs last? What are the determinants of these deviations?
	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
	\item Whether it's a dispute or it's a measure (what does Chad call these?) like AD or escape clause that has not been disputed, it won't be granted for no reason
\end{itemize}
